Typed Lua

### 2013-06-18 doc/slides/gsoc_proposal/gsoc_proposal.tex
Added some statistics to the presentation about the GSoC proposal

>>>>

\subsection{Some Statistics}
\begin{frame}
\frametitle{Some Statistics}
\begin{itemize}
\item Data from LuaRocks as of June 10th
\item 2950 .lua files
\item \textbf{luac} (version 5.2.2) compiles 2864 of the 2950 files
\item We have 2069 files when we ignore files that are generated by
MoonScript and documentation and test subdirectories
\item 18864 functions are being declared
\begin{itemize}
\item 4127 (21.9\%) are actually methods
\item 1586 (8.4\%) use \textbf{type} to inspect the tags of the arguments
\item 771 (4.1\%) return \textbf{nil} plus something else
\item 119 (0.6\%) return \textbf{false} plus something else
\item 549 (2.9\%) use \textbf{setmetatable}
\item 175 (0.9\%) use \textbf{getmetatable}
\end{itemize}
\item The table constructor is used 19049 times
\begin{itemize}
\item 4571 (24.00\%) times is the empty construct
\item 14475 (75.99\%) times is a constructor with only static keys
\item 3 (0.01\%) times is a constructor with only dynamic keys
\item There is no constructor with static and dynamic keys
\end{itemize}
\end{itemize}
\end{frame}
